---
title: "Electronic Health Record Interoperability"
output:
  html_document:
    code_folding: hide
---

```{r setup,include=FALSE}

knitr::opts_chunk$set(message = FALSE,
                      warning = FALSE,
                      fig.width = 6,
                      fig.height = 4)

# need version 1.09+ of data.table
library(data.table)
# additional data manipulation
library(tidyverse)
# ridgeplots
library(ggridges)

# print numbers with 1k sep
comma <- function(x) format(x, digits = 2, big.mark = ",")

```

# {.tabset}

Visualizing interoperability challenges using the meaningful use report
and physician compare dataset to compare hospital and
affiliated physician EHR vendors.

Interoperability impacts healthcare providers, health systems and
patients. While the US healthcare system has made impressive 
strides in the last 8 years, there is still a long way to go.   

## Data 
Two publicly available data sets from the Centers for Medicare
and Medicaid Services:   
  1. [EHR Products Used for Meaningful Use Attestation](https://dashboard.healthit.gov/datadashboard/documentation/ehr-products-mu-attestation-data-documentation.php)  
  2. [Physician Compare National Downloadable File](https://data.medicare.gov/Physician-Compare/Physician-Compare-National-Downloadable-File/mj5m-pzi6)   
  
  
## Definition  

> According to section 4003 of the 21st Century Cures Act, the term 'interoperability,' with respect to health information technology, means such health information technology that— "(A) enables the secure exchange of electronic health information with, and use of electronic health information from, other health information technology without special effort on the part of the user; "(B) allows for complete access, exchange, and use of all electronically accessible health information for authorized use under applicable State or Federal law; and "(C) does not constitute information blocking as defined in section 3022(a)."



```{r MU,cache=TRUE}

# meaningful use reports ----
# cms api url
url.mu <- paste0("http://dashboard.healthit.gov/datadashboard/",
                 "data/MU_REPORT.csv")

# read Meaningful Use report direct from CMS
mu <- fread(url.mu)

total.attest <- nrow(mu)

# create attestation date from date components
mu[, attested := lubridate::make_date(
  as.numeric(Attestation_Year),
  as.numeric(Attestation_Month),
  1L)]

# clean character variables
mu[, Vendor_Name := str_conv(Vendor_Name, "latin1")]
mu[, EHR_Product_Name := str_conv(EHR_Product_Name, "latin1")]
mu[, CCN := ifelse(nchar(CCN) == 5,
                      paste0("0", CCN),
                      as.character(CCN))]
mu[, Id := ifelse(is.na(CCN), NPI, CCN)]

npi.attest <- mu[, 
                 .N,
                 by = .(Id, Attestation_Month, Attestation_Year)]

npi.vend <- mu[,
               length(unique(Vendor_Name)),
               by = .(Id, 
                      Program_Year,
                      Product_Classification, 
                      attested)] 

npi.year <- mu[, .(min(Attestation_Year),
                   max(Attestation_Year)), keyby = Id
               ][, Years := V2 - V1]

mod.attest <- npi.attest[npi.vend[Product_Classification ==
                                    "Modular EHR", .(Id)],
                         on = "Id"][,
                                    Vendors := 
                                      case_when(N == 1 ~ "One",
                                                N == 2 ~ "Two",
                                                N == 3 ~ "Three",
                                                N == 4 ~ "Four",
                                                N == 5 ~ "Five",
                                                TRUE ~ "Six or More")
                                    ][, Vendors := 
                                        factor(Vendors,
                                               levels =
                                                 c("One",
                                                   "Two",
                                                   "Three",
                                                   "Four",
                                                   "Five",
                                                   "Six or More"),
                                               ordered = T)]

```

```{r vendor,cache=TRUE}


expand_yr <- function(x){
  out <- as.numeric(seq(min(x), max(x), 1))
}

vendor.yrs <- mu[,
                 .(expand_yr(Attestation_Year),
                  .N),
                 keyby = .(Id,
                           Vendor_Name,
                           Product_Classification,
                           Provider_Type)]

vendors <- vendor.yrs %>% 
  rename(Attestation_Year = V1) %>% 
  mutate(Vendor_Name = 
           case_when(str_detect(Vendor_Name, 
                                "MEDITECH") ~ "MEDITECH",
                               str_detect(Vendor_Name,
                                          "CPSI|Evident") ~ "CPSI",
                               str_detect(Vendor_Name,
                  "Healthcare Management Sys|HMS") ~ 
                    "MEDHOST",
                               str_detect(Vendor_Name,
                                          "HCA") ~ "HCA",
                               str_detect(Vendor_Name,
                                          "McKesson") ~ "Allscripts",
                               str_detect(Vendor_Name,
                                          "Siemens") ~ "Cerner",
                               TRUE ~ 
                                 str_remove_all(Vendor_Name,
                                          " Corporation|, LLC")))
 
vendor <- vendors %>% 
  group_by(Vendor_Name, Attestation_Year, Provider_Type) %>% 
  summarize(n = n_distinct(Id))

top.vendors <- vendor %>% 
  group_by(Vendor_Name, Provider_Type) %>% 
  summarize(Avg = max(n)) %>% 
  group_by(Provider_Type) %>% 
  mutate(Rank = dense_rank(desc(Avg))) %>% 
  ungroup() %>% 
  mutate(Vendor = ifelse(Provider_Type == "Hospital" & Rank < 6 |
                           Provider_Type == "EP" & Rank <= 8,
                         Vendor_Name, "Other"))

```

```{r Affiliation,cache=TRUE}

# hospital affiliations ----
# Get Physician Compare data via API call to CMS
# will read in all variables as character as CCN5 screws up 
# vartype hueristics
cls <- rep("character", 41)

# call data directly from CMS
aff.hosp <- fread("https://data.medicare.gov/api/views/mj5m-pzi6/rows.csv?accessType=DOWNLOAD", colClasses = cls)

total.docs <- nrow(aff.hosp)

# affiliated column names
ccn <- paste("Hospital affiliation CCN", 1:5)
lbn <- paste("Hospital affiliation LBN", 1:5)

# variables of interest
# limiting identifing variables to Ids
Vars <- c("NPI",
          ccn,
          lbn)

# limit to target variables
aff.hosp <- aff.hosp[, Vars, with = FALSE]

# prepare NPI for matching
aff.hosp <- aff.hosp[, NPI := as.integer(NPI)]

# limit to unique NPI
aff.hosp <- unique(aff.hosp, by = Vars)

# reshape data----
# melt is the equivalent of gather/pivot
aff.hosp <- melt(aff.hosp, measure = patterns("CCN",
                                              "LBN"),
                 value.name = c("MedicareNumber",
                                "Hospital"))
aff.hosp[,variable := NULL]

# limit to providers reporting affiliations
aff.hosp <- aff.hosp[MedicareNumber != "",]

```


```{r merge,cache=TRUE}

aff.hosp2 <- aff.hosp[NPI %in% mu$NPI &
           MedicareNumber %in% mu[!is.na(mu$CCN),]$CCN]

aff.hosp2 <- unique(aff.hosp2)

setkeyv(aff.hosp2, c("NPI", "MedicareNumber"))

mu.ep <- mu[Provider_Type == "EP" &
              NPI %in% aff.hosp2$NPI, .(NPI, Vendor_Name)]

mu.ep <- unique(mu.ep)
  
setkey(mu.ep, NPI)

mu.hosp <- mu[Provider_Type == "Hospital" &
                CCN %in% aff.hosp2$MedicareNumber, 
              .(CCN, Vendor_Name)]

mu.hosp <- unique(mu.hosp)

colnames(mu.hosp) <- c("MedicareNumber", 
                       "Vendor_Name")

setkey(mu.hosp, MedicareNumber)

mu.aff <- aff.hosp2[mu.ep,
                    .(MedicareNumber, Vendor_Name),
                    by = .EACHI]

setkey(mu.aff, MedicareNumber)

mu.aff <- mu.aff[mu.hosp,
               allow.cartesian = T]

mu.aff <- unique(mu.aff)

mu.aff[, Same := i.Vendor_Name == Vendor_Name]

mu.same <- unique(mu.aff[, .(NPI, MedicareNumber, Same)])

aff.cnt <- aff.hosp[,
                    .(length(unique(MedicareNumber))),
                    keyby = NPI]

hosp.cnt <- aff.hosp[,
                    .(length(unique(NPI))),
                    keyby = MedicareNumber]

```

```{r combine,cache=TRUE}

aff.mu.avg <-  mu.aff[,
                     .(length(unique(Vendor_Name)),
                       length(unique(NPI)),
                       mean(Same)),
                       keyby = "MedicareNumber"]

colnames(aff.mu.avg) <- c("MedicareNumber", 
                          "Vendors",
                          "Affiliated", 
                          "InterOp")

aff.mu.npi <- mu.aff[,
                     .(length(unique(i.Vendor_Name)),
                       length(unique(MedicareNumber)),
                       mean(Same)),
                       keyby = "NPI"] 

colnames(aff.mu.npi) <- c("NPI", 
                          "Vendors",
                          "Affiliated", 
                          "InterOp")

aff.mu.disp <- mu.aff[Same == F
                      ][mu[, .I[attested == max(attested)],
           by = .(CCN, Vendor_Name)]$V1][,
                        .(length(unique(MedicareNumber)),
                          length(unique(i.Vendor_Name))),
                        keyby = .(NPI)] 

colnames(aff.mu.disp) <- c("NPI",
                           "Affiliated",
                          "Vendors"
                          )

```

# Interoperability  

Since `r lubridate::month(min(mu$attested), label = T, abbr = F)`
`r lubridate::year(min(mu$attested))`
`r comma(length(unique(mu.aff$NPI)))` 
providers reported their EHR vendor and
affiliation with at least one of
`r comma(length(unique(mu.aff$MedicareNumber)))`
hospitals.

## Hospitals {.tabset}  

### Overall
```{r sct}
aff.mu.avg %>% 
  mutate(grp = "group") %>% 
  ggplot(aes(Affiliated, Vendors))+
  geom_jitter(shape = ".",
              alpha = 3/4)+
  geom_smooth(aes(color = grp),
              show.legend = F,
              size = 1.25,
              span = 1)+
  scale_y_continuous(limits = c(1, 50))+
  scale_x_log10(limits = c(1, 1000))+
  scale_color_viridis_d(begin = 0.0,
                       end = 0.1)+
  labs(title = "Increasing Affiliated Physicians increases EHRs",
       subtitle = 
         paste0("Hospitals with large numbers of affiliated",
                "\nphysicians have to interact with large numbers",
                " of EHRs"),
       x = "log10(Affiliated Physicians)",
       y = "Physician EHR Vendors")+
  theme(panel.background =
          element_rect(fill = "white",
                       colour = "grey50"))
```

### By EHR vendor  
```{r byvend,cache=TRUE}

mu.vend <- mu.aff[, .(length(unique(NPI)),
                      length(unique(Vendor_Name))),
           keyby = .(MedicareNumber, i.Vendor_Name)
           ]

mu.vend <- mu.vend[mu[, .I[attested == max(attested)],
           by = .(CCN, Vendor_Name)]$V1]

mu.vend <- unique(mu.vend)

colnames(mu.vend) <- c("MedicareNumber", 
                       "Vendor_Name",
                       "Affiliated",
                       "Vendors")

mu.vend$Vendor <- case_when(str_detect(mu.vend$Vendor_Name, 
                                "MEDITECH") ~ "MEDITECH",
                               str_detect(mu.vend$Vendor_Name,
                                          "CPSI|Evident") ~ "CPSI",
                               str_detect(mu.vend$Vendor_Name,
                  "Healthcare Management Sys|HMS") ~ 
                    "MEDHOST",
                               str_detect(mu.vend$Vendor_Name,
                                          "HCA") ~ "HCA",
                               str_detect(mu.vend$Vendor_Name,
                                          "McKesson") ~ "Allscripts",
                               str_detect(mu.vend$Vendor_Name,
                                          "Siemens") ~ "Cerner",
                               TRUE ~ 
                                 str_remove_all(mu.vend$Vendor_Name,
                                          " Corporation|, LLC"))

mu.vend <- mu.vend[Vendor %in%
                     top.vendors[top.vendors$Provider_Type ==
                                   "Hospital", ]$Vendor] 

mu.vend %>% 
  ggplot(aes(Affiliated, Vendors))+
  geom_jitter(shape = ".", alpha = 2/3)+
  geom_smooth(aes(color = Vendor), 
              fullrange = T,
              se = F)+
  scale_x_log10()+
  scale_color_viridis_d()+
  guides(color = guide_legend(title = "Hospital\nVendor"))+
  labs(title = "Hospital Vendor Impact",
       x = "log10(Affiliated Physicians)",
       y = "Physician EHR Vendors")+
  theme(panel.background =
          element_rect(fill = "white",
                       colour = "grey50"),
        legend.key.size = unit(2, "lines"))

```

## Providers {.tabset}  

### Overall 
```{r physplots,fig.show="hold",out.width="45%"}

aff.mu.npi %>% 
  filter(Affiliated == 1) %>% 
  mutate(Same = InterOp == 1) %>%
  group_by(Same) %>% 
  summarize(n = n()) %>% 
  ungroup() %>% 
  mutate(label = paste0(round(n / sum(n), 2)*100, "%")) %>% 
  ggplot(aes(Same, n))+
  geom_col(aes(fill = Same), show.legend = F)+
  geom_text(aes(label = label,
                color = Same),
            nudge_y = -5000,
            fontface = "bold",
            size = 5,
            show.legend = F)+
  scale_fill_viridis_d(option = "D",
                       begin = 0.4,
                       end = 0.8)+
  scale_color_viridis_d(direction = -1,
                        option = "D",
                        begin = 0.4,
                       end = 0.8)+
  scale_y_continuous(labels = scales::comma)+
  labs(title = 
         paste(comma(nrow(aff.mu.npi[aff.mu.npi$Affiliated ==
                                       1,])),
       "Physicians reporting a single affiliation"),
       y = "Physicians",
       x = "Reported Use of same EHR as Affiliated Hospital")+
  theme(panel.background =
          element_rect(fill = "white",
                       colour = "grey50"))

aff.mu.npi %>% 
  filter(Affiliated > 1) %>% 
  mutate(Same = InterOp > 0) %>% 
  select(NPI, Same) %>% 
  unique() %>% 
  group_by(Same) %>% 
  summarize(n = n()) %>% 
  ungroup() %>% 
  mutate(label = paste0(round(n / sum(n), 2)*100, "%")) %>% 
  ggplot(aes(Same, n))+
  geom_col(aes(fill = Same), show.legend = F)+
  geom_text(aes(label = label,
                color = Same),
            nudge_y = -3000,
            fontface = "bold",
            size = 5,
            show.legend = F)+
   scale_fill_viridis_d(begin = 0.4,
                       end = 0.8)+
  scale_color_viridis_d(direction = -1,
                        begin = 0.4,
                       end = 0.8)+
 scale_y_continuous(labels = scales::comma)+
  labs(title = 
         paste(comma(nrow(aff.mu.npi[aff.mu.npi$Affiliated !=
                                       1,])),
       "Physicians reporting multiple affiliations"),
       y = "Physicians",
       x = paste0("Reported Use of same EHR ",
                  "as at least 1 Affiliated Hospital"))+
  theme(panel.background =
          element_rect(fill = "white",
                       colour = "grey50"))
```

### Disparate EHR  
```{r dispplot}

aff.mu.disp %>% 
  mutate(Affiliated = factor(Affiliated)) %>% 
  ggplot(aes(x = Vendors, y = Affiliated, 
                      group = Affiliated, fill = ..x..))+
  geom_density_ridges_gradient(scale = 1.2, color = "#FFFFFF") +
  scale_fill_viridis_c()+
  guides(fill = "none")+
  labs(title = "Increasing Affiliations increases EHRs",
       subtitle = 
         paste0("Physicians affiliated with multiple hospitals",
                "\nhave to interact with multiple EHRs"),
       x = "Disparate EHR Vendors",
       y = "Hospital Affiliations") +
 theme(panel.background =
          element_rect(fill = "white",
                       colour = "grey50"))

```

# Vendor Market Share {.tabset}

## Inpatient
```{r inpplot}

n.hosp <- length(
  unique(
    vendors[vendors$Vendor_Name %in%
              top.vendors[top.vendors$Provider_Type ==
                            "Hospital" &
                          top.vendors$Vendor != "Other",
                          ]$Vendor_Name &
              vendors$Provider_Type == "Hospital", ]$Id)
  )

n.ep <- length(
  unique(
    vendors[vendors$Vendor_Name %in%
              top.vendors[top.vendors$Provider_Type !=
                            "Hospital" &
                          top.vendors$Vendor != "Other",
                          ]$Vendor_Name &
              vendors$Provider_Type != "Hospital", ]$Id)
)

vendor %>% 
  inner_join(top.vendors %>% 
               filter(Vendor != "Other") %>% 
               select(Vendor_Name, Provider_Type, Vendor)) %>% 
  filter(Provider_Type != "EP") %>% 
  filter(Attestation_Year < 2018) %>% 
  group_by(Vendor, Attestation_Year) %>% 
  summarize(n = sum(n)) %>% 
  ggplot(aes(Attestation_Year, n))+
  geom_smooth(aes(group = Vendor,
                color = fct_reorder2(Vendor,
                                     Attestation_Year,
                                     n)),
              span = T,
              size = 1.3,
              se = F)+
  scale_y_continuous(labels = scales::comma)+
  guides(color = guide_legend(title = NULL))+
  labs(title = "Hospital Attestations",
       x = "Attestation Year",
       y = "Hospitals",
       caption = paste0("n = ", comma(n.hosp)))+
  scale_color_viridis_d()+
  scale_y_continuous(labels = scales::comma)+
  theme(panel.background =
          element_rect(fill = "white",
                       colour = "grey50"),
        legend.key.size = unit(2, "lines"))

```

## Outpatient  
```{r opplot}

vendor %>% 
  inner_join(top.vendors %>% 
               filter(Vendor != "Other") %>% 
               select(Vendor_Name, Provider_Type, Vendor)) %>% 
  filter(Provider_Type == "EP") %>% 
  filter(Attestation_Year < 2018) %>% 
  group_by(Vendor, Attestation_Year) %>% 
  summarize(n = sum(n)) %>% 
  ggplot(aes(Attestation_Year, n))+
  geom_smooth(aes(group = Vendor,
                color = fct_reorder2(Vendor,
                                     Attestation_Year,
                                     n)),
              span = 1,
              size = 1.3,
              se = F)+
  scale_y_continuous(labels = scales::comma)+
  guides(color = guide_legend(title = NULL))+
  labs(title = "Eligible Provider Attestations",
       x = "Attestation Year",
       y = "Eligible Providers",
       caption = paste0("n = ", comma(n.ep)))+
  scale_color_viridis_d()+
  scale_y_continuous(labels = scales::comma)+
  theme(panel.background =
          element_rect(fill = "white",
                       colour = "grey50"),
        legend.key.size = unit(2, "lines"))

```

# Data 

## Meaningful Use Report {.tabset}

`r comma(length(unique(mu[Provider_Type == "EP"]$NPI)))` Eligible
Providers and
`r comma(length(unique(mu[!is.na(CCN)]$CCN)))` Hospitals made
`r comma(nrow(npi.attest))` attestations to the meaningful use of 
Electronic Health Records from `r min(mu$Attestation_Year)` to
`r max(mu$Attestation_Year)`. Just over half 
(`r round(nrow(npi.year[Years > 2,])/nrow(npi.year),2)*100`%) of
providers attested for 3 or more years.

### Attestations 
```{r muplots,fig.show="hold",out.width="45%"}

npi.attest %>% 
  filter(Attestation_Year < 2018) %>% 
  ggplot(aes(factor(Attestation_Year)))+
  geom_bar(aes(fill = Attestation_Year),
           width = 1,
           color = "#FFFFFF")+
  labs(title = "Attestations by Year",
       x = NULL,
       y = NULL)+
  guides(fill = "none")+
  scale_fill_viridis_c()+
  scale_y_continuous(labels = scales::comma)+
  theme(panel.background =
          element_rect(fill = "white",
                       colour = "grey50"))

npi.vend %>% 
  mutate(Product_Classification =
           ifelse(Product_Classification == "", "Not Reported",
                  Product_Classification)) %>% 
  ggplot(aes(x = factor(1), fill = Product_Classification))+
  geom_bar(width = 1,
           color = "#FFFFFF")+
  labs(title = "Product Classification",
       x = NULL,
       y = NULL)+
  coord_polar(theta = "y", direction = -1)+
  guides(fill = guide_legend(title = NULL))+
  scale_fill_viridis_d()+
  theme_void()

```

### Atypical Attestations   
```{r atyp,fig.show="hold",out.width="45%"}

ggplot(mod.attest,
       aes(x = factor(1), 
           fill = Vendors))+
  geom_bar(width = 1,
           color = "#FFFFFF")+
  labs(title = "Number of Vendors per Modular EHR attestation",
       subtitle = paste0(round(nrow(mod.attest[N > 3]) /
                                 nrow(mod.attest), 2) *100,
                               "% have 4 or more vendors"),
       x = NULL,
       y = NULL)+
  coord_polar(theta = "y", direction = -1)+
  theme_void()
  
atypical <- round(nrow(npi.vend[V1 > 1 & 
          Product_Classification == "Complete EHR"]) /
            nrow(npi.vend[Product_Classification == 
                            "Complete EHR"]), 2)*100

npi.vend[V1 > 1 & 
          Product_Classification == "Complete EHR" , ] %>%
  ggplot(aes(V1))+
  geom_bar(aes(fill = Product_Classification), show.legend = F)+
  labs(title = paste0(atypical,
                      "% of Complete EHR attestations have",
                      " multiple vendors"),
       subtitle = "Complete EHR with 2+ vendors",
         x = "EHR Vendors",
         y = "Attestations")+
  scale_fill_viridis_d()+
  scale_y_continuous(labels = scales::comma)+
  scale_x_continuous(labels = as.integer)+
  theme(panel.background =
          element_rect(fill = "white",
                       colour = "grey50"))

```


## Physician Compare  {.tabset}

`r comma(length(unique(aff.hosp$NPI)))` Providers reported 
affiliations with `r comma(length(unique(aff.hosp$MedicareNumber)))`
hospitals to CMS. The physician compare data contains 
`r comma(total.docs)` records. 

### Hospitals  
```{r haplot}

hosp.cnt %>% 
  mutate(grp = "group") %>% 
  ggplot(aes(V1))+
  geom_histogram(aes(fill = grp),
                 show.legend = F,
                 color = "#FFFFFF")+
  scale_fill_viridis_d(begin = 0.6,
                       end = 0.7)+
  scale_y_continuous(labels = scales::comma)+
  scale_x_continuous(labels = scales::comma)+
  labs(title = "Number of Affiliated Physicians",
       y = "Hospital",
       x = "Affiliated Physicians")+
  theme(panel.background =
          element_rect(fill = "white",
                       colour = "grey50"))

```

### Physician Affiliations
```{r paplot}

aff.cnt %>% 
  group_by(V1) %>% 
  summarise(n = n()) %>% 
  ggplot(aes(V1, n))+
  geom_col(aes(fill = n), 
           color = "#FFFFFF",
           width = 1, show.legend = F)+
  scale_fill_viridis_c(begin = 0.2,
                       end = 0.8)+
  scale_y_continuous(labels = scales::comma)+
  labs(title = "Number of Hospital Affiliations",
       y = "Physicians",
       x = "Hospital Affiliations")+
  theme(panel.background =
          element_rect(fill = "white",
                       colour = "grey50"))

```

